---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# llmcoder

<!-- badges: start -->
[![R-CMD-check](https://github.com/KeiichiSatoh/llmcoder/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KeiichiSatoh/llmcoder/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
This package facilitates the integration of large language models (LLMs), such as ChatGPT, into qualitative data processing and coding workflows. It provides wrapper functions of (mostly) `ellmar` package to streamline interaction between data.frame objects—a standard data structure in R—and LLM-based APIs. 

## Installation

You can install the development version of llmcoder from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
library(pak)
pak::pak("KeiichiSatoh/llmcoder")
```

## Example

This is a basic example to use code_gpt:

```{r example, eval = FALSE}
library(llmcoder)

# Prerequisite:
# You must have a valid OpenAI API key.
# Visit https://platform.openai.com/ to sign up and generate one under
# Dashboard > API Keys.
# Note that running the following example may incur OpenAI API charges.

# Register your API key (temporary session-based)
Sys.setenv(OPENAI_API_KEY = "sk-xxxxxxxxxxxxxxxxx")
# Alternatively, you can store the API key in your .Renviron file to make it persist across sessions.
# As a more convenient option, you can also pass the API key directly as an argument to the `coding_gpt()` function.

# Create a sample data.frame
df <- data.frame(
  ID = 1:3,
  text = c("I like bananas", "I prefer apples", "Grape is the best")
)

# Create a TypeObject that defines the expected structure of the GPT response
type_object_setting <- type_object(
  favorite_fruits = type_string("Extract the speaker's favorite fruits")
)

# Define overall instruction (optional)
overall_instruction <- "Please answer in Japanese."

# Execute the coding
out <- coding_gpt(
  df = df,
  which_col = "text",
  type_object_setting = type_object_setting,
  overall_instruction = overall_instruction
)

# View the coded result
print(out)

```
